---
title: "Battery Recycling"
subtitle: "How can we increase recycling rates"
date: today
author:
  - name: "Gian Teufen"
    orcid: 0009-0002-9355-3503
    email: teufeng@ethz.ch
    affiliation:
      - name: ETH Zurich
        url: https://ethz.ch/de.html

license: "CC BY"
container-title: Research Beyond the Lab
bibliography: bibliography.bib
csl: apa.csl
format:
  html:
    code-fold: true
    toc: true
---

```{r}
#| include: false

library(tidyverse)
library(ggplot2)
library(ggridges)
library(ggthemes)
library(googlesheets4)
library(lubridate)
library(gt)

#get data
tidydata <- read_rds(here::here("data/processed/battery_recycling_incentive_survey_processed_responses.rds"))
```

# Battery Recycling

## Introduction

Because Batteries contain some toxic and valuable components that are even considered critical materials, proper recycling is crucial @2023recycling. Switzerland is the world's No.1 recycling country with an 80% recycling rate of portable batteries, according to @inobat. The government has taken various measures in the past to increase recyling rates. For example they made the separate disposal of used batteries at designated collection points mandatory, the free-of-charge collection of used batteries from any battery consumer is obligatory for any point of sale and public education campaigns were conducted @2006justifications @2009characteristics. Now the question remains of what measures to implement next.

## Methods

A survey was conducted to gather information on the respondents demographics and current recycling behavior, then four different measures were proposed and the respondents were asked to rate each measure on a Likert scale from 1 to 5. They were asked to rate the option "Education campaign" before and after reading the education content to determine whether their knowledge would influence this result. Their previous knowledge was also tested by letting them rate the significance of various consequences of improper battery recycling on a Likert scale.

## Results

Figures and tables in Results section are interpreted with 2 to 3 sentences each; interpretation goes beyond summarizing what is presented and provides context and insight.

-   Introducing a deposit of CHF 0.50 per battery

-   Halving the distance to your next collection point.

-   Education campaigns about the consequences of improper disposal.

-   Batteries can be removed from all devices without tools.

### Rating of Measures

```{r}
#| label: fig-incentive-ratings
#| fig-cap: "The rating of the four proposed measures to increase recycling rates"
#| warning: false

#summarise important cols and only use distinct rows
tidydata_summarized <- tidydata |> 
  summarise(id, measure_type,
            measure_rating) |> 
  distinct()

tidydata_summarized |> 
  ggplot(mapping = aes(x = measure_type,
                     y = measure_rating,
                     fill = measure_type)) +
  geom_boxplot(outlier.shape = NA) +
  scale_x_discrete(labels = c("deposit", "proximity", "education", "removability")) +
  scale_fill_discrete(labels = c("deposit", "proximity", "education", "removability")) +
  labs(x = "Type of Measure", y = "Rating")
```

```{r}
#| include: false

write_csv(tidydata_summarized, here::here("data/final/incentive_ratings.csv"))
```

In @fig-incentive-ratings the support for the various proposed measures can be seen. The most popular choice was to make all batteries removable. This might be connected to the recent public discussion about e-cigarettes and vapes, which famously were allowed to make their batteries non-removeable. The proximity measure was rated the least. This might be because most people dispose of their batteries in supermarkets, where they go to anyways, as can be seen in @fig-disposal_location_education. This figure also shows that people of various levels of education took part in the survey. But it does not show any correlation of this to where they dispose of their batteries.

```{r}
#| label: fig-disposal_location_education
#| fig-cap: "The distribution of where people dispose of their batteries."
#| warning: false

edulocation <- tidydata |> 
  summarise(id,
            disposal_location,
            education_level) |> 
  distinct() |> 
  mutate(disposal_location = recode(disposal_location, "Designated battery bin at Coop, Migros, Denner or Kkiosk" = "Supermarket")) |> 
  mutate(disposal_location = recode(disposal_location, "Electronic waste collection point" = "E-waste site"))
  
edulocation$education_level <- as.character(edulocation$education_level)


edulocation |>
  ggplot(mapping = aes(x = reorder(disposal_location, disposal_location, length), 
                       fill = education_level)) +
  geom_bar() +
  coord_flip() +
  #scale_y_continuous(breaks = seq(from = 0, to = 100, by = 2)) +
  labs(x = "Disposal location",
       y = "Number of responses (total: 35)",
       fill = "Level of education") +
  theme_minimal() +
  scale_fill_colorblind()
```

```{r}
#| include: false

write_csv(edulocation, here::here("data/final/disposal_location_education.csv"))
```

### Correlation current walking distance to proximity measure rating

Another explanation for the low rating of the proximity measure could have been because the people that were interviewed live less than the nationwide average of 500 meters from their disposal site already, as shown in @fig-location-proximity-incentive. But this figure also shows no correlation of people rating the measure higher if they live further away.

```{r}
#| label: fig-location-proximity-incentive
#| fig-cap: "Correlation between walking distance and proximity incentive rating"
#| warning: false

#pivot measure ratings
tidydata_wide <- tidydata |> 
  pivot_wider(names_from = measure_type,
              values_from = measure_rating) |> 
  summarise(id, disposal_location, disposal_distance, distance_incentive_rating) |> 
  distinct()
  

tidydata_wide |> 
  ggplot(aes(x = disposal_distance, y = distance_incentive_rating, color = disposal_location)) +
  geom_point(alpha = 1, size = 3) +
  scale_color_colorblind() +
  labs(x = "Disposal Point Distance",
       y = "Proximity Incentive Rating",
       color = "Disposal Location")

```

```{r}
#| include: false

write_csv(tidydata_wide, here::here("data/final/location_proximity_incentive.csv"))
```

### Importance of Implications

@tbl-implication-importance-ratings lists how important people perceived various implications of non-recycling to be. They mostly name environmental pollution and the loss of critical materials as being the worst consequences.

```{r}
#| label: tbl-implication-importance-ratings
#| warning: false
#| tbl-cap: "Perceived importance of non-recycling implications"

tbldata <- tidydata |>
  summarise(id,
            importance_estimate_type,
            importance_estimate_rating) |> 
  distinct() |> 
  group_by(importance_estimate_type) |>
  summarise(n = n(),
            mean = mean(importance_estimate_rating),
            median = median(importance_estimate_rating),
            sd = sd(importance_estimate_rating)) 

tbldata |> 
  gt() |> 
  fmt_number(columns = c(mean,sd,median),
             decimals = 1) |> 
  opt_stylize(style = 1)
```

```{r}
#| include: false

write_csv(tbldata, here::here("data/final/implication_importance_ratings.csv"))
```

## Conclusions

-   Removable batteries was perceived as the best measure, likely due to public concern over sealed devices like e-cigarettes.

-   Proximity incentives were least favored, as most people already use convenient locations like supermarkets.

<!-- -->

-   No link was found between distance tof disposal sites and support for proximity incentives.

<!-- -->

-   Environmental harm and material loss were seen as the most serious risks of improper disposal.

## References
