---
title: "Battery Recycling"
subtitle: "How can we increase recycling rates"
date: today
author:
  - name: "Gian Teufen"
    orcid: 0009-0002-9355-3503
    email: teufeng@ethz.ch
    affiliation:
      - name: ETH Zurich
        url: https://ethz.ch/de.html

license: "CC BY"
# citation: 
container-title: Research Beyond the Lab
#  url: https://www.example.com # insert website link here
bibliography: bibliography.bib
csl: apa.csl
format:
  html:
    code-fold: true
---

```{r}
#| include: false

library(tidyverse)
library(ggplot2)
library(ggridges)
library(ggthemes)
library(googlesheets4)
library(lubridate)

#get data
tidydata <- read_rds(here::here("data/processed/battery_recycling_incentive_survey_processed_responses.rds"))
```

# Battery Recycling

## Introduction

Because Batteries contain some toxic and valuable components that are even considered critical materials, proper recycling is crucial @2023recycling. Switzerland is the world's No.1 recycling country with an 80% recycling rate of portable batteries @inobat. The government has taken various measures in the past to increase recyling rates. For example they made the separate disposal of used batteries at designated collection points mandatory, the free-of-charge collection of used batteries from any battery consumer is obligatory for any point of sale and public education campaigns were conducted @2006justifications @2009characteristics. Now the question remains of what measures to implement next.

## Methods

A survey was conducted to gather information on the respondents demographics and current recycling behavior, then four different measures were proposed and the respondents were asked to rate each measure on a Likert scale from 1 to 5. They were asked to rate the option "Education campaign" before and after reading the education content to determine whether their knowledge would influence this result. Their previous knowledge was also tested by letting them rate the significance of various consequences of improper battery recycling on a Likert scale.

## Results

Figures and tables in Results section are interpreted with 2 to 3 sentences each; interpretation goes beyond summarizing what is presented and provides context and insight.

-   Introducing a deposit of CHF 0.50 per battery

-   Halving the distance to your next collection point.

-   Education campaigns about the consequences of improper disposal.

-   Batteries can be removed from all devices without tools.

### Rating of Measures

```{r}
#| label: fig-incentive-ratings
#| fig-cap: "The rating of the four proposed measures to increase recycling rates"
#| warning: false

#summarise important cols and only use distinct rows
tidydata_summarized <- tidydata |> 
  summarise(id, measure_type,
            measure_rating) |> 
  distinct()

tidydata_summarized |> 
  ggplot(mapping = aes(x = measure_type,
                     y = measure_rating,
                     fill = measure_type)) +
  geom_boxplot(outlier.shape = NA) +
  scale_x_discrete(labels = c("deposit", "proximity", "education", "removability")) +
  scale_fill_discrete(labels = c("deposit", "proximity", "education", "removability")) +
  labs(x = "Type of Measure", y = "Rating")
```

```{r}
#| include: false

write_csv(tidydata_summarized, here::here("data/final/incentive_ratings.csv"))
```

In @fig-incentive-ratings the support for the various proposed measures can be seen. The most popular choice was to make all batteries removable. This might be connected to the recent public discussion about e-cigarettes and vapes, which famously were allowed to make their batteries non-removeable. The proximity measure was rated the least. Probably because most people dispose of their batteries in supermarkets, where they go to anyways, as can be seen in @fig-disposal_location_education.

```{r}
#| label: fig-disposal_location_education
#| fig-cap: "The distribution of where people dispose of their batteries."
#| warning: false

edulocation <- tidydata |> 
  summarise(id,
            disposal_location,
            education_level) |> 
  distinct() |> 
  mutate(disposal_location = recode(disposal_location, "Designated battery bin at Coop, Migros, Denner or Kkiosk" = "Supermarket")) |> 
  mutate(disposal_location = recode(disposal_location, "Electronic waste collection point" = "E-waste site"))
  
edulocation$education_level <- as.character(edulocation$education_level)


edulocation |>
  ggplot(mapping = aes(x = reorder(disposal_location, disposal_location, length), 
                       fill = education_level)) +
  geom_bar() +
  coord_flip() +
  #scale_y_continuous(breaks = seq(from = 0, to = 100, by = 2)) +
  labs(x = "Disposal location",
       y = "Number of responses (total: 35)",
       fill = "Level of education") +
  theme_minimal() +
  scale_fill_colorblind()
```

```{r}
#| include: false

write_csv(edulocation, here::here("data/final/disposal_location_education.csv"))
```

### Rating of education campaign before & after information

and previous fire knowledge

### Correlation current walking distance to proximity measure rating

```{r}
#| label: location-proximity-incentive
#| fig-cap: "Correlation between walking distance and proximity incentive rating"
#| warning: false

#pivot measure ratings
tidydata_wide <- tidydata |> 
  pivot_wider(names_from = measure_type,
              values_from = measure_rating) |> 
  summarise(id, disposal_location, disposal_distance, distance_incentive_rating) |> 
  distinct()
  

tidydata_wide |> 
  ggplot(aes(x = disposal_distance, y = distance_incentive_rating, color = disposal_location)) +
  geom_point(alpha = 1, size = 3) +
  scale_color_colorblind() +
  labs(x = "Disposal Point Distance",
       y = "Proximity Incentive Rating",
       color = "Disposal Location")

```

```{r}
#| include: false

write_csv(tidydata_wide, here::here("data/final/location_proximity_incentive.csv"))
```

### Another plot

```{r}
#| warning: false
tidydata |> 
  ggplot(mapping = aes(x = disposal_distance, fill = disposal_location)) +
  geom_histogram() +
  facet_grid(disposal_location ~ battery_fires_knowledge, scales = "free_y") +
  scale_fill_colorblind() +
  theme(legend.position = "none")
```

```{r}
#| echo: false
#| results: false
#| output: false


```

## Conclusions

Conclusions concisely summarize findings in a bullet point format.

```{r}

```
